Challenges to transboundary fisheries management in North America under climate change

### 2020-06-12 Ecol/Manuscript_Draft.Rmd
Included S24 code

FigS23 <- readPNG(paste(my_path("F"),"S22.png",sep=""))
grid.raster(FigS22)

@@

<!-- # Explore Regions 4d and 4e -->

>>>>

FigS22 <- readPNG(paste(my_path("F"),"S22.png",sep=""))
grid.raster(FigS22)

@@

<!-- GOMA Outliers analysis -->

```{r FigureS23, eval = T, echo = F, fig.cap = "PChanges in maximum catch potential of yellowtail flounder (Limanda ferruginea) within the study area by mid-century relative to present time. Results for the three global circulation models (GFDL, IPSL, MPIS) used in the current study and two climate change scenarios (Top: High emission – RCP 8.5, Bottom: Low Emission – RCP 2.6). Grid-cells marked in yellow represent discrete areas where average MCP is projected to increase by mid-century."}

FigS24 <- readPNG(paste(my_path("F"),"S24.png",sep=""))
grid.raster(FigS24)

<!-- ESM-DBEM Uncertinty analysis -->

```{r FigureS24, eval = T, echo = F, fig.cap = "Projected MCP change relative to present (2005-2014) for each IPHC regulatory area. Colors represents the different ESM used in the study. Solid line represents a high emission scenario (RCP 8.5) and dashed line represents a low emission scenario (RCP 2.6)"}

FigS24 <- readPNG(paste(my_path("F"),"S24.png",sep=""))
grid.raster(FigS24)
